\documentclass[a4paper]{article}
\usepackage{geometry}
\geometry{left=2cm,right=2cm,top=2.5cm,bottom=2.5cm}
\author{Chunwei Yan}

\title{Beautiful Architecture}
\usepackage{xeCJK}
\usepackage{graphicx}
\setCJKmainfont{SimSun}
%\setCJKmainfont{WenQuanYi Micro Hei Mono}
\begin{document}
    \maketitle
\section{A Tale of Two Systems: A Modern-Day Software Fable}

A software system is like a city -- an intricate network of highways and hostelries, of back roads and buildings.
There's a lot going on in a busy city; flows of control are continually being born, weaving their life through it, and dying.
\par 
if you can learn from these projects' mistakes and success, ou might save yourself (and your software) a lot of pain.

\subsection{Cohesion and Coupline}
Key qualities of software design are cohesion and coupling.
\paragraph{Strong Cohesion}
\par cohesion is a measure of how related functionality is gathered together and how well the parts inside a module work as a whole. cohesion is the glue holding a module together.
\par Weakly cohesive modules are a sign of bad decomposition. Each module must have a clearly defined role, and not be a grab bag of unrelated functionality.
\par 一致性使得一个模块的各个部分能够像一个整体去运行，在这个模块中，每个部分需要有一个特定的明显的角色。
\paragraph{Low Coupling}
Coupling is a measure of the interdependency between modules -- the amount of wiring to and from them.
\par Good sftware design limits the lines of communication to only those that are absolutely necessary. These communication lines are part of what determines the architecture.
\par 为了满足修改和扩充的要求，低耦合能够使系统有更大的灵活性。尽量降低关系的复杂性。
\\
\subsection{Unnecessary coupling}
\par The individual parts of the system were so tightly coupled that you couldn't bring up a skeletal system without creating every single component. 
Any change in a single component rippled out, requiring changes in many dependent components. 
The code components did not make sence in isolation.
\par This made low-level testing impossible, Not only were code-level unit tests impossible to write, but component-level integration tests could not be constructed, as every component depended on almost every other component. 

\textbf{
    Good design takes into account connection mechanisms and the number (and nature) of inter-component connections. 
    The individual parts of a system should be able to stand alone.
    Tight coupling leads to untestable code.
}






\end{document}

